---
title: "IRamesar_Assign10"
author: "Isabel R."
date: "October 29, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Smith is in jail and has 1 dollar; he can get out on bail if he has 8 dollars.A guard agrees to make a series of bets with him. If Smith bets A dollars,he wins A dollars with probability .4 and loses A dollars with probability .6.

Find the probability that he wins 8 dollars before losing all of his money if
#(a) 
He bets 1 dollar each time (timid strategy).

q=.6(Lose)
p=.4(Win)
M = 8

Probability lose=((q/p)^z-(q/p)^M)/(1-q/p)^M
1-((0.6/0.4)^1-(0.6/0.4)^8)/(1-(0.6/0.4)^8)
Probability win=1???Probability lose

```{r}
1-((0.6/0.4)^1-(0.6/0.4)^8)/(1-(0.6/0.4)^8)
```

#(b) 
He bets, each time, as much as possible but not more than necessary tobring his fortune up to 8 dollars (bold strategy).

#Smith needs to bet 3 times to reach $8 - to get from $1 to $2, from $2 to $4 and from $4 to $8. The probability of success for each bet is 0.4, so the probability of 3 successes in a row is:

```{r}
(.4)^3
```


#(c) 
Which strategy gives Smith the better chance of getting out of jail?
Strategy B (Bold strategy) gives Smith a better chance out of getting out of jail, 0.064> 0.020.
