---
title: "Homework5"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A listing of all the values the random variable can assume with their corresponding probabilities make a probability distribution. (https://people.richland.edu/james/lecture/m170/ch06-prb.html). <br/>
Below I use the `runif` dunction to generate random deviates. (https://www.rdocumentation.org/packages/stats/versions/3.6.1/topics/Uniform)

```{r}
B <- runif(10000, min = 0, max =1)
C <- runif(10000, min = 0, max =1)
```

Find the probability that:

##A 
B+C<1/2

```{r}
j = 0
for(i in 1:length(B)){
  if(B[i]+C[i] < .5){
    j = j+1
  }
}
print(j/length(B))
```
In this case, the overall probability is (.25 X .5) = .125.  

##B
BC<1/2

```{r}
j = 0
for(i in 1:length(B)){
  if(B[i]*C[i] < .5){
    j = j+1
  }
}
print(j/length(B))
```

In this problem, the overall probability is 1-(.5^3)= .854.

##C
|B-C|<1/2

```{r}
j = 0
for(i in 1:length(B)){
  if(abs(B[i]-C[i]) < .5){
    j = j+1
  }
}
print(j/length(B))
```
In this problem, the overal probability is 1-2*((.5)^3) = .75. 

##D
max {B,C}<1/2

```{r}
j = 0
for(i in 1:length(B)){
  if(max(c(B[i],C[i])) < .5){
    j = j+1
  }
}
print(j/length(B))
```

In this problem, there is a .75 (1-(.5^2)) chance the minimum of B or C is .5.

##E
min {B,C}<1/2

```{r}
j = 0
for(i in 1:length(B)){
  if(min(c(B[i],C[i])) < .5){
    j = j+1
  }
}
print(j/length(B))
```

This problem, is the compliment to problem D, which is 1-.25=.75.