---
title: "Assign7"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Problem 1
Let X1, X2, . . . , Xn be n mutually independent random variables, each of which is uniformly distributed on the integers from 1 to k. Let Y denote the minimum of the Xi's. Find the distribution of Y.

"Cumulative Distribution Functions (CDF) simply tells us the odds of measuring any value up to and including x. Probability Density Functions (PDF)  is simply the derivative of a CDF. Thus a PDF is also a function of a random variable, x, and its magnitude will be some indication of the relative likelihood of measuring a particular value." (https://www.che.utah.edu/~tony/course/material/Statistics/18_rv_pdf_cdf.php)

***
The cumulative density function of the probability distribution function is:

cdf = (x-1)/(k-1)

Since every x variable n the problem are mutually independent,the probability can be multiplied and applied together.

P(Y<=y) = 1-P(X1> y, ..., Xn > y)
cdf= [1-P(X1> y, ..., Xn > y)]n
cdf= 1-[1-P(X1> y, ..., Xn > y)]n
cdf= 1[1-x-1k-1]n

#Problem 2
 Your organization owns a copier (future lawyers, etc.) or MRI (future doctors).  This machine has a manufacturer's expected lifetime of 10 years.  This means that we expect one failure every ten years.  (Include the probability statements and R Code for each part.).
 
##a
What is the probability that the machine will fail after 8 years?.  Provide also the expected value and standard deviation.  Model as a geometric.  (Hint: the probability is equivalent to not failing during the first 8 years..) 
```{r}
expecteda = 10

probabilitya = 1/expecteda
probabilityfaila = (1- probabilitya)^(8) * probabilitya
probabilityfaila

sda = (1-probabilitya)/(probabilitya^2)
sda
```

The probability that the machine will fail after 8 years is 0.04304672.The standard deviation is 90.

##b
What is the probability that the machine will fail after 8 years?.  Provide also the expected value and standard deviation.  Model as an exponential.
```{r}
probabilityb = exp(-8/10)
probabilityb
```

The probability that the machine will fail after 8 years is 0.449329. The standard deviation is equal to mean, which is 10.

##c
What is the probability that the machine will fail after 8 years?.  Provide also the expected value and standard deviation.  Model as a binomial.  (Hint:  0 success in 8 years).  
```{r}
probabilityc = choose(9, 8) * 0.5^8 * (1 - 0.5)^1
probabilityc

expectedc = 9*0.5
expectedc

sdc = sqrt(9 * 0.5 * (1-0.5))
sdc
```

The probability that the machine will fail after 8 years is 0.0175. The expected value is 4.5, and the standard deviation is 1.5.

##d
What is the probability that the machine will fail after 8 years?.  Provide also the expected value and standard deviation.  Model as a Poisson.
```{r}
ppois(8, lambda = 10, lower.tail = FALSE)

expectedd = 10

sdd = sqrt(10)
sdd
```

The probability that the machine will fail after 8 years is 0.6672. The expected value is 10, and the standard deviation is 3.16.
