---
title: "Week 11 - Assignment"
author: "Isabel R."
date: "November 8, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Assignment

Using the "cars" dataset in R, build a linear model for stopping distance as a function of speed and replicate the analysis of your textbook chapter 3 (visualization, quality evaluation of the model, and residual analysis.)

#Data

```{r}
summary(cars)
```

# Visualization
```{r}
plot(cars$speed, cars$dist, xlab='Speed', ylab='Distance', 
     main='Distance vs. Speed')
```

```{r}
model =lm(formula = dist ~ speed, data = cars)
summary(model)
plot(model)
```

# Conclusion
Speed is estimated to lead to a 3.9 unit increase (Standard Deviation) in distance. This estimate is statistically significant and two variables are nearly normal and appears to be linear. There appears to be a multivariate normality with no multicollinearity. These two variables are independent. The residuals are equal across the regression line.







