---
title: "Homework3"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(pracma)
```

# Problem Set 1

## Question 1

The rank (number of non all-zeros rows) of Matrix A is 4.

```{r}
A = matrix(c(1,-1,0,5,2,0,1,4,3,1,-2,-2,4,3,1,-3),nrow = 4, ncol= 4)
require(Matrix)
rankMatrix(A)[1]
```
or

```{r}
pracma::Rank(A)
```

## Question 2

Since Rank is the number of non all-zeros rows, the maximum rank is m (the number of rows) and the minimum rank of a non-zero matrix is 1.

Example of Maximum Rank
```{r}
Q2ex2 = matrix(c(1,-1,0,5,2,0,1,4,3,1,-2,-2),nrow = 3, ncol= 4)
pracma::Rank(Q2ex2)
```

```{r}
pracma::rref(Q2ex2)
```

Example of Minimum Rank
```{r}
Q2ex1 = matrix(c(0,0,1,0),nrow = 4, ncol= 1)
pracma::Rank(Q2ex1)
```

```{r}
pracma::rref(Q2ex1)
```

## Question 3

The rank (number of non all-zeros rows) of Matrix B is 1.

```{r}
B = matrix(c(1,3,2,2,6,4,1,3,2),nrow = 3, ncol= 3)
pracma::Rank(B)
```

```{r}
pracma::rref(B)
```

\pagebreak

# Problem Set 2

```{r}
A2 = matrix(c(1,0,0,2,4,0,3,5,6),nrow = 3, ncol= 3)
A2
```


```{r}
charpoly(A2)
```

```{r}
eigen(A2) $values
```

```{r}
eigen(A2) $vectors
```

Step by Step Solution on next page.

