---
title: "Homework4"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem Set 1

##Matrix A
```{r}
A <- matrix(c(1,-1,2,0,3,4), nrow = 2, ncol = 3)
A
```

##X

###X = A$A^{T}$ 
```{r}
X = A%*%t(A)
X
```
### X Eigenvalues
```{r}
eigen(X)$values
```

### X Eigenvectors
```{r}
eigen(X)$vectors
```

---

##Y
###Y = $A^{T}$A
```{r}
Y= t(A)%*%A
Y
```

###Y Eigenvalues
```{r}
eigen(Y)$values
```

### Y Eigenvectors
```{r}
eigen(Y)$vectors
```

(https://www.r-bloggers.com/singular-value-decomposition-svd-tutorial-using-examples-in-r/)

##Singular Values 

The singular values of A can be computed by the built-n function `svd` function. 

```{r}
singular<-svd(A)$d
singular
```


##Left Singular Vector
```{r}
Left <- svd(A)$u
Left
```

##Right Singular Vector
```{r}
Right <- svd(A)$v
Right
```

##Examination of Singular Vector 

###Method 1
Upon examining the two sets of singular vectors, the columns of the right singular vector is the eigenvector of Y.

```{r}
Right
eigen(Y)$vectors[,1:2]
```

###Method 2
The examination can also be done by using an `all.equal` function. `all.equal` is a utility to compare R objects x and y testing 'near equality'. (https://www.rdocumentation.org/packages/base/versions/3.6.1/topics/all.equal). The eigenvalues of X and Y should be the same as the square of the Singular Value of A.

```{r}
all.equal(eigen(X)$values,(singular^2))
all.equal(eigen(Y)$values[1:2],(singular^2))
```

#Problem Set 2

##Matrix C
```{r}
C <- matrix(c(1,0,4,3,-1,2,4,2,1), nrow = 3, ncol = 3)
```


##Inverse of a Matrix function
```{r}
myinverse<-function(A){
  n<-ncol(A)
  if(n==nrow(A)){
      #Square Test.
    if(det(A)!=0){
      #Determinant is not zero.
      cofactors<- matrix(0:0,n,n)
      for(i in 1:n){
        for(j in 1:n){
           # For each rows, loop through Column and determine corresponding sub-matrix M_ij, 
           # Find determinant and store in appropriate C[i,j] position.
          detVal<-det(A[-i,-j])
          cofactors[i,j]<- detVal*(-1^(i+j))
        }
      }
      #Inverse calculation co-factor matrix transposition divided by the determinant.
      return(t(cofactors)/det(A))
    }else{
      stop('Determinant is zero.')
    }
  }else{
    stop('Non-square matrix.')
  }
}

myinverse(C)
```

##Inverse of a Matrix function Test
```{r}
solve(C)
```



