---
title: "IRamesar_Assign8"
author: "Isabel R."
date: "October 16, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Problem 11 (Page 303)
A company buys 100 lightbulbs, each of which has an exponential lifetime of 1,000 hours. What is the expected time for the first of these bulbs to burn out?  <br/>

$X_i\sim$ Exp$(\lambda_i)$ then $\min X_i\sim$ Exp$(\sum\lambda_i)$  <br/>
Proof: (http://www.math.wm.edu/~leemis/chart/UDR/PDFs/ExponentialM.pdf)
 
$E[X_i]=\frac{1}{\lambda_i}=1000$, so $\lambda_i=\frac{1}{1000}$.   <br/> 
 
Then $\min X_i \sim$ Exp$(\lambda)$, with $\lambda=\lambda_1+...+\lambda_{100}=\frac{100}{1000}=\frac{1}{10}$.  <br/>  
 
Lastly, $E[\min X_i]=\frac{1}{\lambda}=\frac{1}{1/10}=10$  <br/>

#Problem 14 (Page 303)
Assume that X1 and X2 are independent random variables, each having an exponential density with parameter $\lambda$. Show that Z = X1 - X2 has density fZ(z) = (1/2) $\lambda$ * e - ^($\lambda$|z|) .

First compute the cumulative distribution function (CDF):

$\(P_r\left\{Z \leq z \right\}\)\$

Use the converlution formula, we can write:   <br/>

$\([\begin{equation} \int\limits_{-\infty}^\infty f_{X_1}(x_1)f_{X_2}(x_2)\; \mathrm{d}x = \int\limits_{-\infty}^\infty f_{X_1}(x_1)f_{-X_2}(z-x_1)\; \mathrm{d}x \end{equation}\])\$  

<br/> for discrete random variable, P(-X=-1) = P(X=1), same is true for probability density function (PDF):

$(\(f_{-X_2}(z-x_1) = f_{X_2}(x_1-z)\)\$

Taken together, we have
$\([\begin{equation} f_Z(z) = (1/2)\lambda e^{-\lambda|z|} \end{equation}\])\$

#Problem 1 (Pages 320-321)
Let X be a continuous random variable with mean ?? = 10 and variance $\sigma$ ^ 2 = 100/3. Using Chebyshev's Inequality, find an upper bound for the following probabilities.

(a) P(|X - 10| >= 2)
```{r}
k <- 2/sqrt(100/3)
1/k^2
```

(b) P(|X - 10| >= 5)
```{r}
k <- 5/sqrt(100/3)
1/k^2
```

(c) P(|X - 10| >= 9)
```{r}
k <- 9/sqrt(100/3)
1/k^2
```

(d) P(|X - 10| >= 20)
```{r}
k <- 20/sqrt(100/3)
1/k^2
```

