---
title: "Homework1"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem Set 1

## Question 1

'In mathematics, the dot product or scalar product is an algebraic operation that takes two equal-length sequences of numbers (usually coordinate vectors) and returns a single number. Algebraically, the dot product is the sum of the products of the corresponding entries of the two sequences of numbers.' (https://en.wikipedia.org/wiki/Dot_product)

```{r}
u= c(0.5,0.5)
v= c(3,-4)
dotproduct=u%*%v
dotproduct
```

Or alternatively can be solved, using the following formula:
```{r}
sum(u*v)
```


## Question 2
The computer science defintion of the length would be the following however the mathematical defintion (https://www.khanacademy.org/computing/computer-programming/programming-natural-simulations/programming-vectors/a/vector-magnitude-normalization) of the length would be 0.7071068 and 5 respectively.

Computer Science
```{r}
length(u)
length(v)
```

Mathematical
```{r}
lengthu= sqrt(sum(u*u))
lengthu
```

```{r}
lengthv= sqrt(sum(v*v))
lengthv
```

## Question 3

Arithmetic operations of vectors are performed member-by-member, i.e., memberwise. If we multiply by a number, we would get a vector with each of its members multiplied by that number. Similarly for subtraction, we get new vectors via memberwise operations.  (http://www.r-tutor.com/r-introduction/vector/vector-arithmetics)
```{r}
(3*u)-(2*v)
```


## Question 4

The cosine of the angle between two vectors is equal to the dot product of the vectors divided by the product of vector magnitude also known as vector length.

(https://stackoverflow.com/questions/1897704/angle-between-two-vectors-in-r)
(https://www.math.uh.edu/~jmorgan/Math6397/day13/LinearAlgebraR-Handout.pdf)
(https://onlinemschool.com/math/library/vector/angl/)
(https://onlinemschool.com/math/library/vector/length/)

```{r}
angle= acos((dotproduct)/ (lengthu * lengthv))
angle
```

---

# Problem Set 2

'Gauss-Jordan Elimination is a method of solving a linear system of equations. This is done by transforming the system's augmented matrix (A matrix obtained by appending the columns of two given matrices, usually for the purpose of performing the same elementary row operations on each of the given matrices.) into reduced row-echelon form by means of row operations.' (https://www.mathwords.com/g/gauss-jordan_elimination.htm)
(https://en.wikipedia.org/wiki/Augmented_matrix)

I used the following link to solve  system of equation in R.
(https://www.youtube.com/watch?v=jF71LzipydA)

Testing of Equation Provided
```{r}
A = array(c(1,2,-1,1,-1,-2,3,5,4), dim= c(3,3))
A
b=c(1,2,6)
solve(A,b)
```
System of Equation Function
```{r}
X = array(c(1,1,2,1,-2,1,3,-1,2), dim= c(3,3))
X
y=c(10,-6,10)
solve(X,y)
```


