---
title: "Homework2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem Set 1

## Question 1

I created values to represent the matrix and the transposed matrix.

https://www.basic-mathematics.com/multiply-matrices.html
https://math.hecker.org/2011/05/15/linear-algebra-and-its-applications-exercise-1-6-14/
```{r}
A = matrix(c(1,1,2,4),nrow = 2, ncol= 2)
ATranspose=t(A)
A
ATranspose
```

Here I multipled matrices A and $A^{T}$. https://stat.ethz.ch/R-manual/R-devel/library/base/html/matmult.html
https://www.basic-mathematics.com/multiply-matrices.html

A$A^{T}$ 
```{r}
A%*%ATranspose
```
$A^{T}$A
```{r}
ATranspose%*%A
```

This proves that A$A^{T}$ $\neq$ to $A^{T}$A.

## Question 2

In cases where A is symmertic (A = $A^{T}$) https://en.wikipedia.org/wiki/Symmetric_matrix, A$A^{T}$ = to $A^{T}$A.

```{r}
A2 = matrix(c(2,4,4,1),nrow = 2, ncol= 2)
A2Transpose = t(A2)
A2
A2Transpose
```

Here I multipled matrices A and $A^{T}$. 

A$A^{T}$ 
```{r}
A2%*%A2Transpose
```
$A^{T}$A
```{r}
A2Transpose%*%A2
```
---

# Problem Set 2

A = LU where U is the matrix that we get at the end of the elimination procedure, it is the Upper
Triangular matrix. L is a Lower Triangular matrix and you'll see that the entries of L are
the multipliers that we applied to subtract one row from the other. (Lecture Notes Pg. 3)

https://www.rdocumentation.org/packages/matrixcalc/versions/1.0-3/topics/lu.decomposition
https://www.youtube.com/watch?v=UlWcofkUDDU

```{r}
factorizeLU <- function(A) {
  # Examines if A is square.
  if (dim(A)[1]!=dim(A)[2]) {
    return(NA)
  }
  
  U <- A
  n <- dim(A)[1]
  L <- diag(n)
  
  # If the dimension is one, then U=A and L=[1].
  if (n==1) {
    return(list(L,U))
  }
  
  # Loops through the lower triangle and finds multiplier for each position and adds it to L.
  for(i in 2:n) {
    for(j in 1:(i-1)) {
      multiplier <- -U[i,j] / U[j,j]
      U[i, ] <- multiplier * U[j, ] + U[i, ]
      L[i,j] <- -multiplier
    }
  }
  return(list(L,U))
}
```

```{r}
A <- matrix(c(2,4,4,1), nrow=2, byrow=TRUE)
LU <- factorizeLU(A)
L<-LU[[1]]  
U<-LU[[2]]

A
L
U
A==L %*% U
```


