---
title: "Homework - Week 13"
author: "Isabel R."
date: "November 22, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Question 1

\[ \int4e^{-7x}dx \]

##Answer
Let \(u=-7x\) therefore \(dx=-\frac{1}{7}dz\)

\[ 4\int e^z \frac{-1}{7}dz=\\ \frac{-4}{7}\int e^zdz=\\ -\frac{4}{7}e^z+C=\\ -\frac{4}{7}e^{-7x}+C \]


#Question 2

Biologists are treating a pond contaminated with bacteria. The level of contamination is changing at a rate of \(\frac{dN}{dt}=-\frac{3150}{t^4}-220\) bacteria per cubic centimeter per day, where \(t\) is the number of days since treatment began. Find a function \(N(t)\) to estimate the level of contamination if the level after 1 day was 6530 bacteria per cubic centimeter.

##Answer
\[ \int\frac{dN}{dt}=\int\frac{-3150}{t^4}-220dt=\\ -\frac{12600}{t^3}-220t+C \]

Since \(N(1)=6530\) this can be used to find \(C\).

\[ N(1)=6530=-\frac{12600}{1^3}-220(1)+C\\ C=6290\\ N(t)=-\frac{12600}{t^3}-220t+6290 \]

#Question 3
Find the total area of the red rectangles in the figure below, where the equation of the line is f(x) = 2x+9.

##Answer
\[ \int_{4.5}^{8.5} 2x-9 dx \]

\[ x^2-9x dx |_{4.5}^{8.5} \]


```{r}
((8.5^2)-(9*8.5))-((4.5^2)-(9*4.5))
```

#Question 4

Find the area of the region bounded by the graphs of the given equations, y = x2- 2x- 2,  y = x + 2.

##Answer

\[ x+2=x^2-2x-2\\ =x^2-3x-4\\ =(x-4)(x+1) \]

So the intersections occur at \(x=-1\) and \(x=4\). The area enclosed by these points has \(y=x+2\) above the other equations. So to find the area:

\[x^2 - 2x -2 = x+2\]

\[x^2 -3x -4 = 0\]

\[x = 1, x=-4\]

\[ \int_{-1}^{4} x+2 dx - \int_{-1}^{4} x^2-2x-2 dx \]

\[ (\dfrac{x^2}{2})|_{-1}^{4} - (\dfrac{x^3}{3}-x^2-2x)|_{-1}^{4} \]


```{r}

(8-.5)-((((4*4*4)/3) - 16-8) - (-.3333 -1 + 2))
```


#Question 5

A beauty supply store expects to sell 110 flat irons during the next year. It costs $3.75 to store one flat iron for one year. There is a fixed cost of $8.25 for each order. Find the lot size and the number of orders per year that will minimize inventory costs.

##Answer

```{r}
3.75 * ((110)*(1) - 110) + 8.75*(1)

```

#Question 6

\(int ln(9x) x^6 dx\)

##Answer

\(\int u*dv/dx*dx\) = u*v - \(\int v*du/dx*dx\)

u = ln(9x)

du/dx

u = 9x d/du[ln u * d/dx(9x)] = 1/u* d/dx (9X) = 1/9x * 9
du/dx = 1/x

dv/dx = \(x^6\)
v = \(x^7\)/7

= ln (9x) * \(x^7\)/7 - \(\int x^7/7 * 1/x* dx\) = \(x^7\)*(ln (9x)/7 - 1)

#Question 7

Determine whether f (x) is a probability density function on the interval 1, e6.  If not, determine the value of the definite integral.

##Answer
 \[f(x)= \dfrac{1}{6x}\]

To tell if a function is a probability density function, the integral of the pdf must be equal to 1.

\[\int_{1}^{e^6} \dfrac{1}{6x}\]

\[-\dfrac{1}{6}\int_{1}^{e^6} \dfrac{1}{x}\]

\[-\dfrac{1}{6}ln(x)|_{1}^{e^6}\]

```{r}
((-1/(6))*log(1) - ((-1/(6)*log(exp(6)))))
```

