---
title: "Assignment 3"
date: "February 12, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Homework Questions
3. Copy the introductory example. The vector name stores the extracted names.
R> name
[1] "Moe Szyslak" "Burns, C. Montgomery" "Rev. Timothy Lovejoy"
[4] "Ned Flanders" "Simpson, Homer" "Dr. Julius Hibbert"

```{r}
library(stringr)
raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5543642Dr. Julius Hibbert"
raw.data
```

(a) Use the tools of this chapter to rearrange the vector so that all elements conform to
the standard first_name last_name.
```{r}
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name
```

```{r}
name_remove_title_middle <- str_replace(name, "([[:alpha:]]{1,3}\\.\\s)", "")
name_first_last <- str_replace(name_remove_title_middle, "([[:alpha:]]+), ([[:alpha:]]+)", "\\2 \\1")
name_first_last
```

(b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and
Dr.).

```{r}
str_detect(name, "Dr.|Rev.")
```

(c) Construct a logical vector indicating whether a character has a second name.
```{r}
str_count(str_trim(str_replace_all(name, "Dr.|Rev.", "")), " ") > 1
```


4. Describe the types of strings that conform to the following regular expressions and
construct an example that is matched by the regular expression.
(a) [0-9]+\\$
```{r}
t<-c("test$", "$24$03", 2403)
unlist(str_extract_all(t, "[0-9]+\\$"))
```

(b) \\b[a-z]{1,4}\\b
```{r}
st<-"This is a test of question 4b"
unlist(str_extract_all(st, "\\b[a-z]{1,4}\\b"))
```

(c) .*?\\.txt$
```{r}
tt<-c("test.txt","test.xlsx","test.docx")
unlist(str_extract_all(tt, ".*?\\.txt$"))
```


(d) \\d{2}/\\d{2}/\\d{4}
```{r}
ft<- c("2/12/19","02/12/2019","02/12/19")
unlist(str_extract_all(ft,"\\d{2}/\\d{2}/\\d{4}"))
```

(e) <(.+?)>.+?</\\1>
```{r}
fit<-c("<test>blah</test>","<\test>","<tester>")
unlist(str_extract_all(fit,"<(.+?)>.+?</\\1>"))
```


#Extra Credit
9. The following code hides a secret message. Crack it with R and regular expressions.
Hint: Some of the characters are more revealing than others! The code snippet is also
available in the materials at www.r-datacollection.com.
clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr

```{r}
sc<- "c1copCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf0w3AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPalotfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
extractsc <- unlist(str_extract_all(sc, "[[:upper:]]|[[:punct:]]"))
combinesc <- paste(extractsc, collapse = '')
secretmessage<-str_replace_all(combinesc, "\\.", " ")
secretmessage
```

