---
title: "Assignment 5"
author: "Isabel Ramesar"
date: "February 27, 2019"
output:
    rmdformats::readthedown:
      self_contained: true
      thumbnails: true
      lightbox: true
      gallery: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Create CSV
```{r}
csv <- rbind(c(NA, NA, "Los Angeles", "Phoenix", "San Diego", "San Francisco", "Seattle"),
             c("ALASKA", "On Time", 497, 221, 212, 503, 1841),
             c(NA, "Delayed", 62, 12, 20, 102, 305),
             c("AM WEST", "On Time", 694, 4840, 383, 320, 201),
             c(NA, "Delayed", 117, 415, 65, 129, 61))

write.table(csv, file = "arrivaltimes.csv", sep = ",", col.names=F, row.names=F)
```


#Read CSV into R
```{r}
originalarrival<-read.csv("https://raw.githubusercontent.com/IsARam/DATA607/master/arrivaltimes.csv?_sm_au_=iVVSSF6Sk3kVrtvj")
originalarrival
```

#Transformation Of Data {.tabset .tabset-fade}

##Load Libraries
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
```

##Tidy Data
```{r}
arrival<- originalarrival %>%
mutate(Airlines1 = NA., Airlines2=lag(NA.)) %>% 
mutate(Airline = coalesce(Airlines1,Airlines2), Status = NA..1)  %>%
gather("Destination", "Flights", 3:7) %>% 
select(Airline:Flights) %>% 
arrange(Airline, desc(Status), Destination); arrival
```

I used the following formulas:
1. The `mutate` formula (dplyr) adds new variables and preserves existing. In the case of the above this formula was used to duplicate the first column.
2. The `coalesce` (dplyr) formula finds the first non-missing value at each position.In the case of the above this was used to combine the first and second columns into one.
3. The `gather` formuala (tidyr) takes multiple columns and collapses into key-value pairs, duplicating all other columns as needed.
4. The `select` formula (dplyr) keeps only the variables you mention.
5. The `arrange` formula (dplyr) sort a variable in descending order.

#Analysis {.tabset .tabset-fade}


##Filter Status
```{r}
FlightsDelayed <- arrival %>% group_by(Airline,Destination) %>% filter(Status == 'Delayed') %>%summarise(Delayed = sum(Flights))
FlightsDelayed
```

##Calculate Total Flights
```{r}
TotalFlights <- arrival %>% group_by(Airline,Destination) %>% summarise(Total = sum(Flights))
TotalFlights
```

##Combine and Mutate 
```{r}
DelaySummary<- cbind(FlightsDelayed, Total=TotalFlights$Total)
DelaySummary<- DelaySummary %>% mutate(DelayPercentage = Delayed/Total)
DelaySummary
```

##High Level Summary
```{r}
FlightsDelayedHL <- arrival %>% group_by(Airline) %>% filter(Status == 'Delayed') %>%summarise(Delayed = sum(Flights))
TotalFlightsHL <- arrival %>% group_by(Airline) %>% summarise(Total = sum(Flights))
DelaySummaryHL<-cbind(FlightsDelayedHL,Total=TotalFlightsHL$Total)
DelaySummaryHL<- DelaySummaryHL %>% mutate(HLDelayPercentage = DelaySummaryHL$Delayed/DelaySummaryHL$Total)
DelaySummaryHL
```

Alaska Airlines has a higher delay percentage over AM West however Alaska Airlines had fewer Total Flights.

#Visuals
```{r}
ggplot(DelaySummary, aes(Destination, Delayed)) + geom_point(aes(color=Airline),size=8,alpha=1/2)
```

