---
title: "Data 607 Final Project"
author: "Isabel R."
date: "May 3, 2019"
output: 
  html_document:
    theme: united
    highlight: espresso
    number_sections: TRUE
    toc:  true
    toc_float:  true
    code_folding: show
---

Topic: Suicide Analysis

#Background
***
Suicide is death caused by injuring oneself with the intent to die. Suicide is associated with several risk and protective factors, is connected to other forms of injury and violence, and causes serious health and economic consequences.  Suicide is the second leading cause of death in the world  and tenth leading cause of death in the Unites States. Suicide affects the health of others and the community.

I would like to use the tools acquired from this class to future understand and analyze suicide trends for a given time period to determine suicide patterns within given Countries (Population, GDP), Sexes and Ages. 

I would like to understand the attributes of people who commit suicide and determine if there are any correlations.

I would like to explore questions such as:<br>
.	What are the top three country with the highest suicide rates?<br>
.	Are GDP and Country Happiness and suicide rate correlated?<br>

My belief is that Suicide is more prevalent in Asian countries and that countries with a higher happiness rate has lower suicide rates.

#Data Sources and Loading into R
***

##CSV
[Kaggle.com] https://www.kaggle.com/russellyates88/suicide-rates-overview-1985-to-2016#master.csv	<br>
```{r}
suicide <- read.csv("https://raw.githubusercontent.com/IsARam/DATA607/master/suicideoverview.csv?_sm_au_=iVVNj7S11w7JFQDV", header=TRUE,sep = ",", stringsAsFactors = FALSE)
```

[Kaggle.com] https://www.kaggle.com/unsdsn/world-happiness <br>
```{r}
wh <- read.csv("https://raw.githubusercontent.com/IsARam/DATA607/master/worldhappiness.csv?_sm_au_=iVVNj7S11w7JFQDV", header=TRUE,sep = ",", stringsAsFactors = FALSE)
```

##Web Scrape
[International Monetary Fund] https://www.imf.org/external/pubs/ft/weo/2019/01/weodata/weorept.aspx?sy=2015&ey=2015&ssd=1&sort=country&ds=.&br=1&pr1.x=57&pr1.y=14&c=922%2C158%2C111&s=NGDPD&grp=0&a= <br>

```{r}
library(rvest)
library(XML)
countrygdp<- read_html("https://www.imf.org/external/pubs/ft/weo/2019/01/weodata/weorept.aspx?sy=2015&ey=2015&ssd=1&sort=country&ds=.&br=1&pr1.x=57&pr1.y=14&c=922%2C158%2C111&s=NGDPD&grp=0&a=&")
countrygdp %>%
  html_nodes("tr:nth-child(4) td+ td , tr:nth-child(5) td:nth-child(1)") %>%
  html_text()
```

```{r}
x <- c( "Japan", "Russia", "United States")
y <- c( 4,389.476, 1,363.707, 18,219.300)
cg <- data.frame( "Country" = x, "GDP" = y)
ncg<-cg [c(1,3,5),]
ncg
```


#Data Transformation 
***

##Libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse) 
library(knitr)
library(dplyr)
library(plyr)
library(tidyr)
library(ggplot2) 
library(plyr) 
library(rvest) 
library(XML)
```

##Wrangle Data 
While the data that was loaded has Suicide numbers going back to 1987, I wanted to hone my analysis on Suicide % (Suicide Number/Total Population) for the top three countries, focusing primarily on 2016. Conduting data transformation using `filter`,`select`, `group_by`, `summarise`, `arrange` and `mutate`, I was able to determine that the top three countries with the highest Suicide Percentage in 2015 was Lithuania, Korea and Slovenia.


```{r}
head(suicide)
```

ns %>% group_by(country) %>% summarise(Total_Suicide=sum(suicides_no,na.rm = TRUE),Total_Population=sum(population,na.rm = TRUE)) %>% mutate(Suicide_Percentage=Total_Suicide/Total_Population

```{r}
library(plyr)
library(dplyr)
newsuicide<-suicide %>% filter(year==2015)
ns<-select(newsuicide,country,suicides_no,population)
n2s<-ns %>% 
group_by(country) %>% 
dplyr::summarise(Total_Suicide=sum(suicides_no,na.rm = TRUE),Total_Population=sum(population,na.rm = TRUE)) %>% 
mutate(Suicide_Percentage=(Total_Suicide/Total_Population))
n2s<-n2s %>% arrange(desc(Suicide_Percentage))
head(n2s,3)
```

Not accounting for population, conduting data transformation using `filter`, `select`, `group_by`, `summarise` and `arrange`,the top three countries with the highest total amount of Suicide was Unites States, Russia and Japan. For the purpose of my analysis, I will look at the countries with the highest Total Suicide not accounting for Population (United States, Russia and Japan).In order to do a mutating join I will need to transform country name **Russian Federation** to **Russia** in the top3 table. I also renamed column name for **country** to **Country** using the `names` function. 

```{r message=FALSE}
newsuicide<-suicide %>% filter(year==2015)
ns<-select(newsuicide,country,sex,age,suicides_no)
n3s<-ns %>% group_by(country) %>% summarise(Total_Suicide=sum(suicides_no,na.rm = TRUE))
n3s<-n2s %>% arrange(desc(Total_Suicide))
top3<-n3s[1:3,]
top3$country <-revalue(top3$country, c("Russian Federation"="Russia"))
names(top3)[1]<-"Country"
top3
```

For the purpose of my analysis, I will look at the countries with the highest Total Suicide not accounting for Population (United States, Russia and Japan). 

```{r}
worldhappiness<-wh %>% filter(Year==2015, Country %in% c("United States","Russia","Japan")) %>% select(Country, Happiness.Rank, Happiness.Score, Health..Life.Expectancy.)
worldhappiness
```

I will perform a mutating Join to combine all three data sets. A mutating join allows you to combine variables from two tables. It first matches observations by their keys, then copies across variables from one table to the other.I used a `left_join` function which return all rows from x, and all columns from x and y. 
```{r}
join <- left_join(top3,worldhappiness)
join
ncg
newjoin <-left_join(join,ncg)
```




```{r}
countrygdp
```


```{r}
maxPages <- round((req$response$meta$hits[1] / 10)-1) 
pages <- list()
for(i in 0:maxPages){
  nytSearch <- fromJSON(paste0(url, "&page=", i), flatten = TRUE) %>% data.frame() 
  message("Retrieving page ", i)
  pages[[i+1]] <- nytSearch 
  Sys.sleep(1) 
}
allNYTSearch <- rbind_pages(pages)
```

```{r}
datatable(allNYTSearch, extensions = 'Buttons', options = list(
  dom = 'Bfrtip',
  buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
```

#Data Validation
***

##Statistical Analysis 

 I want to determine if there is a correlation between 
```{r}
cor()
```


##Visualization 




#Conclusion
***

##Statistical Analysis - Support Conclusion

##Visualization - Support Conclusion

FEATURE NOT COVERED IN CLASS [There are many examples:  "I used ggmap; I created a decision tree; I ranked the results; I created my presentation slides directly from R; I figured out to use OAuth 2.0."]
I would like to explore Shiny.


#References
***
https://stat545.com/bit001_dplyr-cheatsheet.html#left_joinpublishers-superheroes
