---
title: "Different datasets"
date: "March 10, 2019"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
---
##Load Libraries
```{r eval=TRUE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(knitr)
```


#Data Set 1

Topic: Avocado Prices <br />
Posted by: Samriti Malhotra <br />
URL: http://www.hassavocadoboard.com/retail/volume-and-price-data <br />

##Create a .CSV file and Read .CSV into R

I combined both Conventional and Organic 2018 tables into one table.
```{r echo=FALSE}
avocadoprices<-read.csv("HAB_Retail_Volume_and_Price_2018_conventional&organic_TotalUS.csv", sep = ",")
head(avocadoprices)
```


```{r eval=FALSE}
avocadoprices<-read.csv("https://raw.githubusercontent.com/DATA607/master/avocado.csv",sep=",")
head(avocadoprices)
```

##Tidy Data {.tabset .tabset-fade}

I am using `tidyr` to tidy data.

###Rename Column Names

I wanted to rename columns names to make the table more readable.
```{r}
colnames(avocadoprices)
```

```{r}
colnames(avocadoprices)<- c("Type", "Date", "AveragePrice","TotalVolume","Product4046", "Product4225"   , "Product4770", "TotalBags", "SmallBags","LargeBags","XLargeBags")
head(avocadoprices)
```

###Gather Data
I wanted to create a column for volume type. A common problem is a dataset where some of the column names
are not names of variables, but values of a variable.
```{r eval=TRUE}
avocadoprices<-avocadoprices %>% gather("Product4046","Product4225","Product4770", "TotalBags", "SmallBags","LargeBags","XLargeBags", key="VolumeType", value = "Volume")
head(avocadoprices)
```
###Seperate Data
I wanted to distinguish the Date Column primarily summarizing within the month.
```{r eval=FALSE}
avocadoprices<-avocadoprices %>% separate(Date, into = c("Year","Month","Date"), sep="-")
head(avocadoprices)
```

##Data Transformation {.tabset .tabset-fade}

I am using `dplyr` to transform data.

###Descriptive Statistics
```{r}
summary(avocadoprices)
```

###Analysis

    Which Avocado type has the highest total volume, conventional or organic?
    Conventional Avocado's has a higher Total Volume over Organic.
```{r eval=TRUE}
avocadobytype<-
avocadoprices %>%
  group_by(Type) %>%
  summarize(TotalVolume = sum(TotalVolume))
avocadobytype
```

```{r eval=TRUE}
ggplot(avocadobytype)+ geom_point(aes(Type,TotalVolume)) + labs(x="Type",Y= "Total Volume")
```
   
    Which month has the Highest Volume?
    April has the highest month of Total Volume sold.
 
code chunk works in Console however when Knitting I get the following error: `Error: Column ` avocadoprices$Month` is unkown`

```{r eval=FALSE}
avocadobymonth<-avocadoprices %>%group_by(avocadoprices$Month) %>% summarize(TotalVolume = sum(TotalVolume))
avocadobymonth
```

```{r eval=FALSE}
ggplot(avocadobymonth)+ geom_point(aes(Month,TotalVolume)) + labs(x="Month",Y= "Total_Volume")
```


#Data Set 2
Topic: Cold and Heat Absorbtion<br />
Posted by: Christopher Ayre<br />


##Create a .CSV file and Read .CSV into R

```{r echo=FALSE}
abs<-read.csv("science proj data.csv")
head(abs)
```


```{r eval=FALSE}
abs<-read.csv("https://raw.githubusercontent.com/DATA607/master/science%20proj%20data.csv",sep = ",")
head(abs)
```
 
##Tidy Data  {.tabset .tabset-fade}

###Rename Column Names
```{r}
colnames(abs) <- c("color",0,10,20,30,40,50,60,"phase")
```

###Gather Data
I wanted to convert the table from a wide format to a long format by using `gather`. Upon using the `str` function, I discovered that time was stored as a chr data type so I need to convert newabs$time to a numeric data type.
```{r eval=TRUE}
newabs<-gather(abs, time, temperature, "0":"60")
str(newabs)
newabs$time <- as.numeric(newabs$time)
str(newabs)
head(newabs)
```


##Data Transformation {.tabset .tabset-fade}

###Descriptive Statistics
```{r eval=TRUE}
summary(newabs)
```

###Analysis

```{r eval=TRUE}
ggplot(newabs)+ geom_point(aes(newabs$color,newabs$temperature)) + labs(x="Color",Y= "Temperature")
```


#Data Set 3

Topic: Top Best Seller Books on Amazon<br />
Posted by: Henry otuadinma<br />

##Create a .CSV file and Read .CSV into R

```{r}
books<- read.csv("topBooks.csv",sep=",")
head(books)
```

```{r}
str(books)
```

##Tidy Data  {.tabset .tabset-fade}

I am using `tidyr` to tidy data. I will only be working with the total columns as opposed to the quarterly data focusing on Region.

###Subset Data and Rename Column Names
```{r}
colnames(books)<- c("Title", "Author", "Genre","Rating","Image", "Rating"   , "Type", "Price")
colnames(books)
```

```{r}
newbooks<- subset(books, select = c(1:4))
newbooks
```
```{r}
newbookswona<-na.omit(newbooks)
newbookswona
```

###Gather Data

##Data Transformation {.tabset .tabset-fade}

After subsetting the table, this table is in an ideal form to analyze. 

###Descriptive Statistics
```{r}
summary(newbookswona)
```

###Analysis 

```{r eval=TRUE}
avgratingbygenre<-
newbookswona %>%
  group_by(Genre) %>%
  summarize(AverageRating = mean(Rating))
avgratingbygenre
```
```{r}
qplot(x = avgratingbygenre$Genre, y = avgratingbygenre$AverageRating, data = avgratingbygenre, geom="point")
```

Religion appears to be the highest rated Genre and Literature & Fiction appear to be the lowest rated Genre.

