---
title: "Data 607 Final Project"
author: "Isabel R."
date: "May 12, 2019"
output: 
  ioslides_presentation:
      widescreen: true
---

#Background
***
Suicide is death caused by injuring oneself with the intent to die. Suicide is associated with several risk and protective factors, is connected to other forms of injury and violence, and causes serious health and economic consequences.  Suicide is the second leading cause of death in the world  and tenth leading cause of death in the Unites States. Suicide affects the health of others and the community.

I would like to use the tools acquired from this class to future understand and analyze suicide trends for a given time period to determine suicide patterns within given Countries (Population, GDP), Sexes and Ages. 

I would like to understand the attributes of people who commit suicide and determine if there are any correlations.

I would like to explore questions such as:<br>
.	What are the top three country with the highest suicide rates?<br>
.	Is GDP and suicide rate correlated?<br>

#Data Sources and Loading into R

##CSV
[Kaggle.com](https://www.kaggle.com/russellyates88/suicide-rates-overview-1985-to-2016#master.csv)	<br>
```{r}
suicide <- read.csv("https://raw.githubusercontent.com/IsARam/DATA607/master/suicideoverview.csv?_sm_au_=iVVNj7S11w7JFQDV", header=TRUE,sep = ",", stringsAsFactors = FALSE)
```

[Kaggle.com](https://www.kaggle.com/unsdsn/world-happiness) <br>
```{r}
wh <- read.csv("https://raw.githubusercontent.com/IsARam/DATA607/master/worldhappiness.csv?_sm_au_=iVVNj7S11w7JFQDV", header=TRUE,sep = ",", stringsAsFactors = FALSE)
```

##Web Scrape
[International Monetary Fund](https://www.imf.org/external/pubs/ft/weo/2019/01/weodata/weorept.aspx?sy=2015&ey=2015&ssd=1&sort=country&ds=.&br=1&pr1.x=57&pr1.y=14&c=922%2C158%2C111&s=NGDPD&grp=0&a=) <br>

```{r warning=FALSE, message=FALSE, eval=FALSE}
library(rvest)
library(XML)
countrygdp<- read_html("https://www.imf.org/external/pubs/ft/weo/2019/01/weodata/weorept.aspx?sy=2015&ey=2015&ssd=1&sort=country&ds=.&br=1&pr1.x=57&pr1.y=14&c=922%2C158%2C111&s=NGDPD&grp=0&a=&")
countrygdp %>%
  html_nodes("tr:nth-child(4) td+ td , tr:nth-child(5) td:nth-child(1)") %>%
  html_text()
```

```{r message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
Country <- c("Japan", "Russia", "United States")
GDP <- c(4,389.476, 1,363.707, 18,219.300)
countryGDPDF<- data.frame(Country,GDP)
cgdf<-countryGDPDF [c(1,3,5),]
cgdf
```


#Data Transformation 

##Libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse) 
library(knitr)
library(dplyr)
library(plyr)
library(tidyr)
library(ggplot2) 
library(plyr) 
library(rvest) 
library(XML)
```

##Wrangle Data 
While the data that was loaded has Suicide numbers going back to 1987, I wanted to hone my analysis on Suicide % (Suicide Number/Total Population) for the top three countries, focusing primarily on 2016. Conduting data transformation using `filter`,`select`, `group_by`, `summarise`, `arrange` and `mutate`, I was able to determine that the top three countries with the highest Suicide Percentage in 2015 was Lithuania, Korea and Slovenia.

```{r}
library(plyr)
library(dplyr)
newsuicide<-suicide %>% filter(year==2015)
ns<-select(newsuicide,country,suicides_no,population)
n2s<-ns %>% 
group_by(country) %>% 
dplyr::summarise(Total_Suicide=sum(suicides_no,na.rm = TRUE),Total_Population=sum(population,na.rm = TRUE)) %>% 
mutate(Suicide_Percentage=(Total_Suicide/Total_Population))
n2s<-n2s %>% arrange(desc(Suicide_Percentage))
head(n2s,3)
```
##Wrangle Data
Not accounting for population, conduting data transformation using `filter`, `select`, `group_by`, `summarise` and `arrange`,the top three countries with the highest total amount of Suicide was Unites States, Russia and Japan. For the purpose of my analysis, I will look at the countries with the highest Total Suicide not accounting for Population (United States, Russia and Japan).In order to do a mutating join I will need to transform country name **Russian Federation** to **Russia** in the top3 table. I also renamed column name for **country** to **Country** using the `names` function. 

```{r message=FALSE}
newsuicide<-suicide %>% filter(year==2015)
ns<-select(newsuicide,country,sex,age,suicides_no)
n3s<-ns %>% group_by(country) %>% summarise(Total_Suicide=sum(suicides_no,na.rm = TRUE))
n3s<-n2s %>% arrange(desc(Total_Suicide))
top3<-n3s[1:3,]
top3$country <-revalue(top3$country, c("Russian Federation"="Russia"))
names(top3)[1]<-"Country"
top3
```

##Wrangle Data
For the purpose of my analysis, I will look at the countries with the highest Total Suicide not accounting for Population (United States, Russia and Japan). 

```{r}
worldhappiness<-wh %>% filter(Year==2015, Country %in% c("United States","Russia","Japan")) %>% select(Country, Happiness.Rank, Happiness.Score, Health..Life.Expectancy.)
worldhappiness
```

##Wrangle Data
I performed a mutating join to combine all three data sets.It first matches observations by their keys, then copies across variables from one table to the other.I used a `left_join` function which return all rows from x, and all columns from x and y. 
```{r warning=FALSE}
join <- left_join(top3,worldhappiness)
TopSuicide <-left_join(join,cgdf)
TopSuicide
```

#Data Validation

##Data Summary
```{r}
summary(TopSuicide)
```

##Correlation
 I want to determine if there is a correlation between suicide totals and GDP for the top three countries United States, Russia and Japan. From my result, it appears that there is a negative correlation which means that both variables move in the opposite direction.
```{r}
cor(TopSuicide$Total_Suicide,TopSuicide$GDP)
```

Looking at all the countries, the correlation between suicide totals and GDP appear to be positive. A positive correlation means there is a positive relationship between the variables, as one variable increases or decreases, the other follows the same direction.
```{r}
cor(newsuicide$suicides_no,newsuicide$gdp_per_capita....)
```

##Boxplot of Top Suicide Total
```{r}
newsuicide %>% filter(country ==c("United States","Russian Federation","Japan")) %>% ggplot(aes(x = gdp_per_capita...., y = suicides_no, color = factor(country))) + geom_boxplot(alpha=0.5) + ggtitle("Plot of Suicide Rate and GDP")
```

##Boxplot of Suicide by Country
```{r}
newsuicide %>% ggplot(aes(x = gdp_per_capita...., y = suicides_no, color = factor(country))) + geom_boxplot(alpha=0.5) + ggtitle("Plot of Suicide Rate and GDP")
```

##Box Plot of Suicide Rate By Country
```{r}
newsuicide %>% boxplot(suicides_no ~ country, data = ., main="Boxplot of Suicide Rate", ylab = "Suicide Rate per 100,000", xlab = "Country", col = "lightblue")
```
##GDP Historgram and QQNORM Plot
```{r}
hist(newsuicide$gdp_per_capita...., main = "GDP", col = "lightblue")
qqnorm(newsuicide$gdp_per_capita...., main = "QQ Plot of GDP")
```

##Scatter Plot of Suicide Total and GDP
```{r}
ggplot(newsuicide, aes(x = gdp_per_capita...., y = suicides_no)) + geom_jitter(alpha = 0.3) + geom_smooth(lwd = 0.85, alpha = 0.15) + ggtitle("Scatter Plot of Suicide Total and GDP")
```
##Suicide Rate and GDP
```{r}
newsuicide %>% filter(country ==c("United States","Russian Federation","Japan")) %>% ggplot(aes(x = gdp_per_capita...., y = suicides_no, color = factor(country))) + geom_boxplot(alpha=0.5) + ggtitle("Plot of Suicide Rate and GDP")
```


#Conclusion

##Summary
```{r}
summary(lm(newsuicide$gdp_per_capita....~newsuicide$suicides_no,data=newsuicide))
```

##Correlation
```{r}
cor.test(newsuicide$gdp_per_capita...., newsuicide$suicides_no, method = "pearson")
```

##Conclusion
Suicide cases by country can be explored using statistical tools. Per previous graphs it was shown on the previous graphs that there is a non-linear relationship between the Suicide Rates and the Country's GDP per capita. Based on the statistical analysis,it can be assumed that there is no relationship between the Country's Suicide Cases and the GDP per capita.It is not statistically significant to support that GDP per capita of one's country contributes to the suicide cases.Since p value 0.06889 is > 0.05, this means that the data used do not fit the linear regression model and can be assumed that there is no relationship between the Country's Suicide Cases and the GDP.

Although GDP does not directly impact suicide cases, this could be one of the many contextual reasons as it relates to economic aspects.

#References

##Links
[Dplyr Cheat Sheet](https://stat545.com/bit001_dplyr-cheatsheet.html#left_joinpublishers-superheroes) <br>
[Kaggle.com](https://www.kaggle.com/russellyates88/suicide-rates-overview-1985-to-2016#master.csv)	<br>
[Kaggle.com](https://www.kaggle.com/unsdsn/world-happiness) <br>
[IMF](https://www.imf.org/external/pubs/ft/weo/2019/01/weodata/weorept.aspx?sy=2015&ey=2015&ssd=1&sort=country&ds=.&br=1&pr1.x=57&pr1.y=14&c=922%2C158%2C111&s=NGDPD&grp=0&a=) <br>
[Rpubs.com](https://rpubs.com/beancounter/430586)

Thank You.

