---
title: "Project 1 - Chess Tournament Data"
author: "Isabel Ramesar"
output:
  html_document:
    css: ./lab.css
    highlight: pygments
    theme: cerulean
    pdf_document: default
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Instructions
Create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) with the following information for all of the players:Player's Name, Player's State, Total Number of Points, Player's Pre-Rating, and Average Pre Chess Rating of Opponents.


#Load Data {.tabset .tabset-fade}


## Reading Into R

```{r}
library(stringr)

tournament <- readLines("https://raw.githubusercontent.com/IsARam/DATA607/master/tournamentinfo.txt", warn = FALSE)
```

## Display Table 
```{r}
head(tournament)
```

# Tidy Data {.tabset .tabset-fade}


##Row Identification
```{r}
line1 <- c(seq(5,length(tournament),by=3))
line2 <- c(seq(6,length(tournament),by=3))
```

##Extract & Scrubing
```{r}
name <- str_replace_all(str_extract(tournament[line1],"([|]).+?\\1"),"[|]","")
state <- str_trim(str_extract(tournament[line2],"[[:blank:]]+\\w+"))
points <- str_sub(tournament[line1],str_locate(tournament[line1],"[.]")[1]-1,str_locate(tournament[line1],"[.]")[1]+1)
prerating <- as.numeric(str_extract(str_sub(tournament[line2],str_locate(tournament[line2],":")[1],str_locate(tournament[line2],">")[1]),"[[:digit:]]+"))
```


##Data Frame Creation
```{r}
tournamentrows <- data.frame(name,state,points,prerating, stringsAsFactors = FALSE)
head(tournamentrows)
```

# Data Manipulation {.tabset .tabset-fade}

##Average Pre-Rating Per Player
```{r}
oppavgrate <- NULL
for (i in seq(5,length(tournament),by=3))
{oppavgrate <- c(oppavgrate, as.integer(mean(tournamentrows$prerating[c(as.numeric(unlist(str_extract_all(str_sub(tournament[i], start=51),"[[:digit:]]+"))))])))}
```

##Append To Dataframe
```{r}
tournmanettable <- cbind(tournamentrows,oppavgrate)
head(tournmanettable)
```

# CSV {.tabset .tabset-fade}
 
```{r}
# Write CSV in R
write.table(tournmanettable, file = "tournamentinfo.csv",row.names=FALSE, na="",col.names=TRUE, sep=",")
```

#Visualization {.tabset .tabset-fade}

##Group and Summarize
```{r message=FALSE}
library(dplyr)
tournamentbystate <-group_by(tournmanettable, state)
tournamentbystate <-summarize(tournamentbystate, meanpre = mean(prerating),meanoppavg = mean(oppavgrate))
```

##Plot
```{r}
library(ggplot2)

ggplot(tournamentbystate, aes(x=state, y=meanpre)) + 
  geom_col(color="dark green",fill="dark green")+ 
  labs(title ="Rating by State", 
       x = "State", 
       y = "Average Rating") 
```

