---
title: "Project 2 - Preparing different datasets"
author: "Isabel Ramesar"
date: "March 10, 2019"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
---
##Load Libraries
```{r eval=FALSE}
library(xml2)
library(rvest)
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(RColorBrewer)
```


#Data Set 1

Topic: Avocado Prices <br />
Posted by: Samriti Malhotra <br />
URL: http://www.hassavocadoboard.com/retail/volume-and-price-data <br />

##Create a .CSV file and Read .CSV into R

I combined both Conventional and Organic 2018 tables into one table.

```{r echo=FALSE}
avocadoprices<-read.csv("HAB_Retail_Volume_and_Price_2018_conventional&organic_TotalUS.csv", header=TRUE)
head(avocadoprices)
```


```{r eval=FALSE}
avocadoprices<-read.csv("https://raw.githubusercontent.com/IsARam/DATA607/master/HAB_Retail_Volume_and_Price_2018_conventional%26organic_TotalUS.csv?_sm_au_=iVVr1ZHQL3QjSSsP",sep=",")
head(avocadoprices)
```

##Tidy Data {.tabset .tabset-fade}

I am using `tidyr` to tidy data.

###Rename Column Names

I wanted to rename columns names to make the table more readable.
```{r}
colnames(avocadoprices)
```
```{r}
colnames(avocadoprices)<- c("Type", "Date", "AveragePrice","TotalVolume","Product4046", "Product4225"   , "Product4770", "TotalBags", "SmallBags","LargeBags","XLargeBags")
head(avocadoprices)
```

###Gather Data
I wanted to create a column for volume type. A common problem is a dataset where some of the column names
are not names of variables, but values of a variable.
```{r}
avocadoprices<-avocadoprices %>% gather("Product4046","Product4225","Product4770", "TotalBags", "SmallBags","LargeBags","XLargeBags", key="VolumeType", value = "Volume")
head(avocadoprices)
```
###Seperate Data
I wanted to distinguish the Date Column primarily summarizing within the month.
```{r}
avocadoprices<-avocadoprices %>% separate(Date, into = c("Year","Month","Date"), sep="-")
head(avocadoprices)
```

##Data Transformation {.tabset .tabset-fade}

I am using `dplyr` to transform data.

###Descriptive Statistics
```{r}
summary(avocadoprices)
```

###Analysis & Visuals

    Which Avocado type has the highest total volume, conventional or organic?
    Conventional Avocado's has a higher Total Volume over Organic.
```{r}
avocadobytype<-
avocadoprices %>%
  group_by(Type) %>%
  summarize(TotalVolume = sum(TotalVolume))
avocadobytype
```

```{r}
ggplot(avocadobytype)+ geom_point(aes(Type,TotalVolume)) + labs(x="Type",Y= "Total Volume")
```
   
    Which month has the Highest Volume?
    April has the highest month of Total Volume sold.
```{r}
avocadobymonth<-
avocadoprices %>%
  group_by(Month) %>%
  summarize(TotalVolume = sum(TotalVolume))
avocadobymonth
```


```{r}
ggplot(avocadobymonth)+ geom_point(aes(Month,TotalVolume)) + labs(x="Month",Y= "Total Volume")
```


#Data Set 2

Topic: Immigration and Adjustment Status<br />
Posted by: Debabratra Kabiraji<br />
URL: https://www.dhs.gov/immigration-statistics/special-reports/legal-immigration<br />

```{r echo=FALSE}
permres<-read.csv("FY2018_Q3_Tables_Final_D correctedPermRes.csv", header=TRUE)
permres
```

##Create a .CSV file and Read .CSV into R

```{r eval=FALSE}
permres <-read.csv("https://raw.githubusercontent.com/IsARam/DATA607/master/FY2018_Q3_Tables_Final_D%20correctedPermRes.csv?_sm_au_=iVVr1ZHQL3QjSSsP",sep=",")
head(permres)
```


##Tidy Data  {.tabset .tabset-fade}

I am using `tidyr` to tidy data. I will only be working with the total columns as opposed to the quarterly data focusing on Region.

###Subset Data and Rename Column Names
```{r}
newpermres<- permres[c(7:13),c(1,2,7,12)]
colnames(newpermres)<-c("Region","Total","Adjustments","New")
newpermres
```

###Gather Data
I wanted to create a column for permanent resident status. A common problem is a dataset where some of the column namesare not names of variables, but values of a variable.
```{r}
newpermrestidy<-newpermres %>% gather("Adjustments","New",key="Status", value = "Amount")
newpermrestidy<-select(newpermrestidy,"Region","Status","Amount")
newpermrestidy
```
##Data Transformation {.tabset .tabset-fade}

###Descriptive Statistics
```{r}
summary(newpermrestidy)
```

###Analysis & Visuals

 Which is the highest status reason?

```{r}
permresbystatus<-
newpermrestidy %>%
  group_by(Status) %>%
  summarize(Amount = sum(Amount))
permresbystatus
```
```
 


###Visual

#Data Set 3
Topic: Train Accident Data<br />
Posted by: Isabel Ramesar<br />
URL:https://safetydata.fra.dot.gov/officeofsafety/publicsite/on_the_fly_download.aspx<br />


##Create a .CSV file and Read .CSV into R
  

```{r eval=FALSE}
trainaccident<-read.csv("https://raw.githubusercontent.com/IsARam/DATA607/master/NYRailEquipmentAccident_Incident.csv?_sm_au_=iVVVFSP6Vn7Q4Sps",sep=",")
head(trainaccident)
```

##Tidy Data  {.tabset .tabset-fade}

###Rename Column Names

###Gather Data

###Seperate Data

##Data Transformation {.tabset .tabset-fade}

###Descriptive Statistics

###Analysis & Visuals


###Analysis
Analysis Requested:<br />

    How many accidents per month? 
    Which railroad had the most accidents?
    Which county has the most accidents?
    Do accidents occur most in AM or PM?


